mixchar

### 2018-08-01 README.Rmd
modify logo size
add banner!
resize banner

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "100%"
)
```

```{r top_banner, echo=FALSE, fig.height=3, fig.width=4}
knitr::include_graphics('logo/mixchar_logo.png')
```

>>>>

<img src = "logo/mixchar_banner.png" height="350" width="350" />

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
